\documentclass{cultvoucher}
\usepackage{cultvoucher}

\addbibresource{pubs.bib}
\addtocategory{papers}{backgrounds,p20paper}
\addtocategory{books}{rudin}
\addtocategory{professional}{autocomplete,ccc}
\addtocategory{presentations}{ceu15,gcurs16,tug19}
\addtocategory{workshops}{nyulatex}


\begin{document}\thispagestyle{firststyle}

\begin{adjustwidth}{\dimexpr-\marginparsep-\marginparwidth}{}
	\begin{center}
		{\Huge \textsc{\texttt{Nathaniel T. Stemen}}\par}
		\href{mailto:nate@stemen.email}{\texttt{nate@stemen.email}} \textbullet{}
		\href{https://natestemen.xyz}{\texttt{natestemen.xyz}}
		\rule{\dimexpr\textwidth+\marginparsep+\marginparwidth}{0.4pt}\par
	\end{center}
\end{adjustwidth}

\section{Education}
\rhsentry{University of Waterloo}{2020--}{Ph.D.\ in Applied Mathematics (Quantum Information)}

\rhsentry{New York University}{2013--2017}{B.Sc.\ in Mathematics and Physics}
\begin{itemize}
	\item Thesis in Mathematics: \href{https://github.com/natestemen/q-vortex-thesis}{\textit{An Investigation of \(\mathcal{Q}\)-Balls}}
	      \begin{itemize}
		      \item Advisor: Prof.\ Luciano Medina
	      \end{itemize}
	\item Dean's List (\textit{cum laude})
	\item University Honors Scholar
\end{itemize}

\section{Employment \& Research}
\lhsentry{Software Developer}
{\href{https://www.overleaf.com/}{Overleaf}, London \& New York City}
{July 2017--current}
\begin{itemize}
	\vspace{-0.25em}
	\item Provided data for and built new \LaTeX{} autocomplete feature using
	      machine learning techniques such as cosine similarity, decision trees,
	      and neural networks.
	\item Maintained large \keyword{Rails} and \keyword{Node} web applications
	      by providing bug fixes and feature improvements.
	      % \item Collected and presented company data to use as a starting point for
	      %       data driven decisions on the companies business model and new feature
	      %       development.
	\item Attended conferences as a company representative to interact with and
	      gather customer feedback from Overleaf users.
	\item Extracted and analyzed data for The Connected Culture of Collaboration
	      Report. An analysis of collaborative scholarly writing to be published
	      in 2020.
\end{itemize}

\lhsentry{Undergraduate Researcher}
{New York University}
{May 2016--May 2017}
\begin{itemize}
	\vspace{-0.25em}
	\item Studied nonlinear Schr\"{o}dinger equations modeling transmission of
	      short electromagnetic pulses in nonlinear media under Prof.\
	      \href{https://www.sites.google.com/a/nyu.edu/luciano-medina/}{Luciano Medina}
	      and Dr.\ \href{https://cims.nyu.edu/~esposito/}{Joseph Esposito}.
	\item Numerically computed solutions to nonlinear partial differential
	      equations using \keyword{python} and analytically proved existence of
	      solutions.
\end{itemize}

\lhsentry{Summer Researcher}
{Yale University (\href{http://prospect.yale.edu/}{\small{PROSPECT Experiment}})}
{Summer 2014 \& 2015}
\begin{itemize}
	\vspace{-0.25em}
	\item Completed R\&D for detector that is performing eV-scale sterile
	      neutrino search and measuring the antineutrino spectrum from the
	      nuclear reactor at Oak Ridge National Laboratory under Prof.\
	      \href{http://heegerlab.yale.edu/karsten-heeger}{Karsten Heeger} and
	      Dr.\ \href{https://www.physics.sjtu.edu.cn/en/people/1/kehan}{Ke Han}.
	\item Built optical simulation using \keyword{C++} of a prototype detector
	      to study light collection, detector uniformity, and optimize light
	      guide shape.
	\item Surveyed and implemented pulse-shape discrimination methods in
	      \keyword{python} to determine optimal method for neutrino event
	      selection.
\end{itemize}

\lhsentry{Orientation Leader}
{New York University}
{Summer 2014 \& 2015}
\begin{itemize}
	\vspace{-0.25em}
	\item Worked with a partner orientation leader guiding groups of 25 new
	      students through NYU's orientation week.
	\item Organized, coordinated, and facilitated events encouraging new
	      students to socialize and discover NYU and NYC.
\end{itemize}

\section{Publications}
\printbib{papers}
\printbib{books}
\printbib{professional}

\section{Talks}
\printbib{presentations}
\printbib{workshops}

\section{Teaching}
\lhsentry{Mathematics Teacher}{{\small NYU Metro Center College Prep Academy}}{June--August 2016}
\begin{itemize}
	\vspace{-0.25em}
	\item Independently planned and taught Pre-Calculus course for high school
	      students.
	\item Created and graded in class worksheets, quizzes, and homework.
	\item Used the Moore Method to guide students through advanced topics and
	      introduce the idea of rigor in mathematics.
\end{itemize}

\lhsentry{Mathematics Tutor}{{\small NYU Metro Center College Prep Academy}}{October 2015--May 2017}
\begin{itemize}
	\vspace{-0.25em}
	\item Facilitated numerous extra-curricular math courses of 30 students as
	      a class assistant by providing additional guidance to students.
\end{itemize}

\section{Conferences Attended}
\lhsentry{Joint Mathematics Meeting}{Denver, CO}{January 2020}

\lhsentry{\href{https://www.tug.org/tug2019/}{\TeX{} Users Group}}{Palo Alto, CA}{August 2019}

\lhsentry{Joint Mathematics Meeting}{Baltimore, MD}{January 2019}

\lhsentry{MathFest}{Denver, CO}{August 2018}

\lhsentry{\#FuturePub}{North Carolina State University}{April 2018}

\lhsentry{\href{https://web.northeastern.edu/het/string_data/}{String Data}}{Northeastern University}{November 2017}

\lhsentry{Gulf Coast Undergraduate Research Symposium}{Rice University}{October 2016}

\lhsentry{Fall Meeting of the APS Division of Nuclear Physics}{Santa Fe, NM}{October 2015}

\section{Affiliations}
\rhsentry{Mathematical Association of America}{2018--current}{}

\lhsentry{Sigma Pi Sigma}{Physics Honors Society}{2015--current}

\rhsentry{American Physical Society}{2014--current}{}

\lhsentry{Society of Undergraduate Physicists}
{{\small{President, Vice-President, Secretary.}}}
{2014--2017}
\begin{itemize}
	\item Planned weekly events with talks from students, alumni, professors,
	      and professionals.
	\item Planned and organized fundraising events such as Fermi Estimation
	      with over 40 attendees.
\end{itemize}

\section{Academic Activities}
\lhsentry{Readings in Spectral Graph Theory}{Courant Institute}{Spring 2017}
\begin{itemize}
	\item Met with group of 5 students and Professor weekly to discuss current
	      research topics in graph theory.
\end{itemize}

\lhsentry{Foundations and Philosophy of Quantum Mechanics}{NYU}{2016--2017}
\begin{itemize}
	\item Co-organized group of 15 students that met weekly to discuss the
	      mathematical and philosophical foundations of quantum mechanics at
	      NYU.
\end{itemize}

\section{Continued Education}
\rhsentry{Docker Mastery: with Kubernetes \& Swarm from a Docker Captain}{}{}
\begin{itemize}
	\item Learned how to use Docker to build development environments with code
	      running in containers for interoperability.
	\item Verification: \url{https://ude.my/UC-HGBK3LSJ}
\end{itemize}
\rhsentry{Presenting Data and Information}{November 2019}{}
\begin{itemize}
	\item Covered fundamental design strategies for information displays
	      such as tables, diagrams, charts, images, and other data
	      visualizations.
	\item Taught by \href{https://www.edwardtufte.com/tufte/}{Edward Tufte}.
\end{itemize}
\lhsentry{Cryptography I}{\href{https://www.coursera.org/learn/crypto}{Coursera}}{Ongoing}
\begin{itemize}
	\item Online course about the inner workings of cryptographic primitives
	      and how to reason about security.
	\item Taught by \href{https://crypto.stanford.edu/~dabo/}{Dan Boneh}, Stanford University.
\end{itemize}

\section{Languages}
\begin{itemize}
	\item Python, JavaScript, SQL, Ruby, Mathematica, C++, HTML
	\item English (native), Mandarin Chinese (beginner)
\end{itemize}

\end{document}
